---
title: "DATA607_Assignment SQL and R"
author: "Gabriel Santos"
date: '2022-09-10'
output:
  html_document: default
  pdf_document: default
---

```{r }
library(tidyverse)
```

### *Calling the necessary packages*

```{r }
library(DBI)
library(RMySQL)
library(RODBC)
```

### *Establish MySQL connection*

```{r }
mydb = dbConnect(MySQL(), user='root', password='Sysadm123', dbname='movie_data', host='localhost')
```

### *Table list*

```{r }
dbListTables(mydb)
```

### *Table fields*

```{r }
dbListFields(mydb, 'movie_data.people')
dbListFields(mydb, 'movie_data.movies')
dbListFields(mydb, 'movie_data.PeopleMoviesRatings')
dbListFields(mydb, 'movie_data.PeopleMovieRatingsResults')
```

```{r }
PeopleMoviesRatings = dbSendQuery(mydb, "select * from movie_data.PeopleMoviesRatings")

```

### *Fetch table people from database*

```{r }
PeopleMoviesRatings = fetch(PeopleMoviesRatings, n = 5)
print(PeopleMoviesRatings)                
```

### *movies table fields*

```{r }

```

## *Reading a csv file to R*

#### *I exported my sq data into a csv file and I placed the csv file on Github. I then made R read the csv file on Github.* 

```{r }
mysql <- read.csv("https://raw.githubusercontent.com/GabrielSantos33/DATA607-Assignment-2/main/movie_ratings.csv",header=TRUE,sep=",")
head(mysql)
```

### *Average Rating of Movies My Friends Watched*

#### *I first filtered out the null values and then I had to make the chr values under Stars into integer values to calculate the average.To know the average rating among the movies my friends had seen.*

```{r}
avg_mov <- mysql %>%
  group_by(movie) %>%
  filter(Stars != "NULL") %>%
  summarise(avg= mean(as.integer(Stars)))
avg_mov
```
### *Spider-Man was watched by all my friends and they also rated it very highly with a rating of 4.8*

```{r }
library(ggplot2)
ggplot(data=avg_mov, aes(x=movie,y=avg , fill=movie)) + 
  coord_flip() +
  geom_bar(stat="identity")
```

## *Movies my Friends did not watched and how many didn’t watch.*

### *Movies my friends did not watch so I aggregated the data by movie, I filtered the condition where the stars were null and I counted how many people did not watch the movies.*

### *4 of my friends did not watch No Time to Die and one of my friend did not watch dune.*

```{r }
nul <- mysql %>%
  group_by(movie) %>%
  filter(Stars=="NULL") %>%
  count(Stars,sort=TRUE)
nul
```


## *Results*

```{r }
library(ggplot2)
ggplot(data=nul,aes(x=movie,y=n,fill=movie)) +
  geom_bar(stat="Identity")
```